Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-31 msbr_reproc.tex
grammar"

The method approximate a single representative unit cell for the whole 
\gls{MSBR} core, consequently, it does not take into consideration different 
fuel-moderator volume ratio for Zone I, Zone II, annulus, and reflector. The 
initial multiplication factor during depletion calculation is selected for 
state with fully withdrawn control and poison rods position which gives high 
excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{keff.png}
        \caption{Infinite multiplication factor during 4 years depletion 
        simulation.}
        \label{fig:keff}
\end{figure}

@@

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{fuel_composition.png}
        \caption{Normalized number density of major isotopes during 4 years 
        depletion.}
        \label{fig:compos}
\end{figure}

>>>>

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
state with fully withdrawn control and poison rods position which gives high 
excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{keff.png}
        \caption{Infinite multiplication factor during a 4-years depletion 
        simulation.}
        \label{fig:keff}
\end{figure}

@@

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{fuel_composition.png}
        \caption{Normalized number density of major isotopes during 4 years of 
        depletion.}
        \label{fig:compos}
\end{figure}
